\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Noah A. Ehrman}
\address{ 5426 Albany Ct. \\ Fort Wayne, IN 46835  }
\address{ 260~$\cdot$~267~$\cdot$~1541 \\ noah.a.ehrman@gmail.com }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Education}
    {\bf R. Nelson Snider High School} \hfill {\em June 2019} \\ 
    { Academic Honors Diploma } \\
    Overall GPA: 3.9

    {\bf Indiana University Bloomington} \hfill {\em March 2023} \\ 
    { B.S. Computer Science } \\
    Current GPA: 3.552
  \end{rSection}
  
  \begin{rSection}{Experience}
  
	  \begin{rSubsection}{Fort Wayne Tincaps}{March 2018 - September 2018}{Concessions Backcoutner}{Fort Wayne, IN}
	\item Perparing and serving food to baseball fans attending games at Parkview field.
	\item Maintaining the cleanliness of my concession stand and the general area around it.
	\item Assisting customers in meeting their specific needs through precise and clear communication.
	\item Coordinating with my fellow backcounter workers to quickly and efficiently serve customers.
	\end{rSubsection}

	\begin{rSubsection}{Meijer Inc}{November 2018 - July 2019}{Parking Lot Attendant}{Fort Wayne, IN}
	\item Ensured that Meijer customers would always have carts available at the store entrance.
	\item Took out trash and recycling at the front of the front of the store as needed, keeping an eye on both as I performed my main duty.
	\item Listened for calls to return items to shelves and load items into customers' vehicles.
	\item Worked persistently through the hottest and coldest days of 2019.
	\end{rSubsection}

	\begin{rSubsection}{Indiana University Bloomington}{November 2019 - March 2020}{Dining Hall Student Worker}{Bloomington, IN}
	\item Preparing and serving a wide variety of food to fellow students in an IU dining hall.
	\item Dining hall was split into several sections each with their own menu and workflow. Every time I entered a new section I quickly learned this way of working.
	\item Coordinating with fellow student workers and full-time workers to ensure food was always in stock, customers were always being served, and our section was always clean.
	\end{rSubsection}
  
  \end{rSection}
  
  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
 	Computer Lnguages & Java, C\#, Python, Lua, Lisp/Scheme, HTML, CSS, SQL \\
	Operating Systems & Windows, Linux, Mac OS, Android \\
 	Tools & Vim, VSCode/Visual Studio, IntelliJ, Git, Bash
    \end{tabular}
  \end{rSection}

\end{document}
